Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-07-31 writing/nips_submission/response/EML_response.tex
More tweaks

\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for the meta-mapping that operates over polynomials (e.g. multiplying by 2). Specifically, a set of polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding for each one. We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another. Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a probe polynomial through $F$ to produce a predicted output. The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task; in meta training, we used an $\ell^2$ between the predicted task embedding and the embedding of the target task. One of the main algorithmic insights of our work is that this produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig. 3). To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$, by feeding the predicted function embedding to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs. We hope this clarifies our approach, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge. Notably, because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model. (We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well. However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, provide exciting future directions. For now, we are revising the main text to clarify our message. \par 

@@

\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary. We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, this will be important future work. On the DQN: the problem is not exactly a standard supervised problem because you have multiple betting actions and only observe the reward for the bet you execute, we have clarified this in the text. \par 

@@

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 61.0\% on 5-shot, 5-way classification, competitive with e.g. MAML. We expect that with more than a few days to tune hyperparameters and refine the model we could do much better. \par

>>>>

\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of embeddings of input polynomials and output polynomials for a meta-mapping that operates over polynomials (e.g. multiplying by 2). Specifically, a set of polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding for each one. We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another. Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a novel probe polynomial through $F$ to produce a predicted output, which is the embedding of a novel function obtained by transforming the input polynomial. The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task; in meta training, we used an $\ell^2$ loss between the predicted task embedding and the embedding of the target task. One of the main algorithmic insights of our work is that this loss produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig. 3). To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output embedding matched $2x + 4$, by feeding it to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs. We hope this clarifies our approach, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge, by using the same computational structure for both basic tasks and meta-mappings. Because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model. (This actually performs better than having separate networks for basic tasks and meta-mappings, see appendix D.1.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well. However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, could be exciting future directions. For now, we are revising the paper to clarify our message. \par 

@@

\textbf{Architecture:} We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, this will be important future work. Cards/DQN: this is not exactly a supervised problem because you have multiple betting actions and only observe the reward for the one you take, we have clarified this in the text. \par 

@@

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 61.4\% on 5-shot, 5-way classification, competitive with MAML and Meta-LSTM. We expect that with more than a few days to tune and refine the model we could do much better. \par
